---
title: "Package Overview"
author: "Chris Taber"
date: "2019-06-06"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(knitr)
library(buildingRpackages)
```


This Package includes functions used to read in and map accident data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. 

## Functions

**fars_read** This is a simple function that imports a csv file as a tibble dataframe. The function check if the file exists, and if it does, reads in the file and converts it to a tbl_df. An error will occur if filename doe not exist.

**make_filename** This function take a year, converts it to an interger, and prints the new file name with the year appended to the end as a character vector (eg. "accident_1996.csv.bz2"). A warning will occur if year is not supplied as a numeric value.

**fars_read_years** This function take a vector or list of years and creates a filename for all years provided. Provides an error message if invalid year supplied.

**fars_summarize_years** This funtion returns a tibble for each Year and Month combination that counts the total rows for each month, with each year as its own column.

**fars_map_state** This function returns a plot of all accidents in a state for the year provided. An error will occur if invalid state.num provided. If no accidents exist for state.num and year provided, a message will be reutrned stating this.



**Example of *fars_read*:**
```{r echo=TRUE}
filename <- system.file('extdata', 'accident_2013.csv.bz2', package = 'buildingRpackages')
fars_read(filename)
```


**Example of *fars_read_years*:**
```{r echo=TRUE}
fars_read_years(c(2013,2014))
```

**Example of *fars_summarize_years*:**
```{r echo=TRUE}
fars_summarize_years(c(2013, 2014))
```


**Example of *fars_map_state*:**
```{r echo=TRUE}
fars_map_state(1,2013)
fars_map_state(10,2014)
```

